Environmental Parameters

### 2023-03-22 code/analysis_code/analysis_README.Rmd
Added distribution stats

This folder contains code for analyzing cleaned data sets and aids in visualization of parameters of interest.\
(1) The dust subfolder contains `daily_dust.qmd`, which looks at dust concentration over the daily time series. It also contains `dust_and_copies.qmd` which combine Vibrio enumeration with dust data.\
(2) The env sub-folder contains `env_par.qmd` that examines temperature and salinity over the time series.\
(3) The qPCR sub-folder contains `daily_qmd` that has data on Vibrio enumeration. This is also seen in the `dust_and_copies.qmd` in the dust subfolder \
(4) The stats folder contains `dust_copies_stats.qmd` that runs models on variables of interest. \

>>>>

This folder contains code for analyzing cleaned data sets and aids in visualization of parameters of interest.\
(1) The dust subfolder contains `daily_dust.qmd`, which looks at dust concentration over the daily time series. It also contains `dust_and_copies.qmd` which combine Vibrio enumeration with dust data.\
(2) The env sub-folder contains `env_par.qmd` that examines temperature and salinity over the time series.\
(3) The qPCR sub-folder contains `daily_qmd` that has data on Vibrio enumeration. This is also seen in the `dust_and_copies.qmd` in the dust subfolder \
(4) The stats folder contains:
- `distributiom.qmd`: Checks distribution of variables of interest
- `multi_variate.qmd`: runs multivariate models on variable of interest (copies_mL)
- `uni_variate.qmd` : runs univariate models on variable and predictors of interest.
